Recruiting Chapter

### 2021-06-12 text/manuscript_june_2021.Rmd
your side

@@

DESCRIBE HOW TO READ TABLE AND WHAT THE RESULTS SHOW

INSERT TABLE X ABOUT HERE

Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network. Generally -- whether graphing one-mode or two-mode networks -- network graphs show vertices as circles and edges as lines connecting pairs of vertices. In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a dotted line -- if both universities visit at least one high school in common.

For our one-mode public

Network graphs show vertices as nodes and edges as lines connecting two nodes. Conceptually, we think of nodes as repelling one another and edges as pulling nodes together. Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together. Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.  In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure.

We also address research question 3 by using cluster analysis to identify colleges/universities that share common network structure. Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties. Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups. We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits

@@

>>>>

The University of Alabama -- and to a lesser extent the University of South Carolina and CU-Boulder -- is omnipresent in the private high schools visited by the other public research universities in our sample, except the University of Nebraska-Lincoln. For the remaining universities, Figure \@ref(tab:pubu-percent-matrix) suggests several clusters of universities. For example, UMass-Amherst, Suny Stonybrook and Rutgers tend to visit many of the same high schools, as do University of Arkansas and the University of Kansas.

@@

INSERT TABLE \@ref(fig:plot-1mode-pubu) ABOUT HERE

Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network. Generally -- whether graphing one-mode or two-mode networks -- network graphs show vertices as circles and edges as lines connecting pairs of vertices. In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common. The width of a solid line between universities indicates the number of high schools both universities visited. Finally, the shape of each university vertex is determined by cluster analysis, which we specified to allocate each university to one of four groups, based purely on network patterns.

@@

Figure \@ref(fig:plot-1mode-pubu) shows three universities in the cneter of the recruiting network, the University of Alabama -- a cluster unto itesf -- and the University of South Carolina and CU-Boulder.  By contrast, the University of Nebraska-Lincoln, UC-Riverside, and SUNY-Stonybrook are on the periphery of the network. These three universities are members of the same community cluster, despite not visiting any high schools in common. Between this most peripheral and the most central of universities, lies a cluster of 9 universities, consisting largely of universities that enoll relatively few out-of-state students but are actively seeking more.
